%!TEX root = ../Main.tex
Concluding on section \cref{theorysec,hamilsec,greensec,transec}, simple numerical methods have been developed and implemented with success. The resulting LDOS, band and transmission plots, especially for NPG, show that the method indeed is capable of reproducing results from DFT and TBtrans calculations. However, there are small discrepancies in the results obtained when comparing with DFT. The reasons for the discrepancy is not immediately clear from the results but there might be a couple of things to point out and keep in mind. The method has been developed on the assumption that all atoms are in the plane and they, as a baseline, all have the same potential. This might cause some of the small differences that one can see in the results, especially the transmission plots of \cref{transmissionplots}. So the DFT approach might have picked up some these effects that the developed method could not.\\
In \cref{testsec} the program showed that it too could reproduce results of much more complicated systems with multiple atom species, not just carbon. Some of the initial results where not strongly resembling the DFT calculations, but after some tweaking of specific on-site potentials, the agreement became clear. This gave some valuable insights as to what happens chemically in NPG when it is functionalised with different atoms. These discoveries also made it more clear which flaws the method had and how to go about simulating even more complicated systems. One approach which should be implemented is automating the manipulation of the on-site potentials of species bonded to the bridges in NPG. The scripts used in this project only took into account the specific atoms bonded to the NPG and changed their potential. However, as one can see in potential maps in the figures of \cref{testsec}, the potential is not only changing at the specific sites where the atoms have bonded. It also changes the on-site potential of all the other atoms in the system. This was not accounted for in the developed method. However, there is a system as to how these potentials change. In future work, a possible way to account for the potential change, is to look at each carbon atom in the system and see which atoms it bonds to. If carbon is bonded to e.g. hydrogen the potential increases. If its bonded to electron withdrawing atoms e.g. oxygen, the potential decreases significantly. So by looking at each carbon atom, checking which species of atoms it bonds to, it would be possible to assign the correct potential to that atom. Going through the whole system this way would yield even more precise results. Practically we utilise SISL when importing the geometry. We could further the import process by creating list of species indices and use that information to automatically assign more fitting potentials.\newline
This proposal is for working out the details of producing the most accurate results possible.\newline
The main conclusion is that the project succeeded in making a program that could reproduce results that qualitatively was the same as the DFT, but in a much simpler way. This should pave the way for faster computing of all different kinds of NPG systems in a field that is still evolving rapidly. By showing a method where DFT has been avoided, it also gives a more intuitive understanding of electron transport within NPG systems. The scripts will help for the rational design of chemically tailored NPGs as potential platforms for future nano circuitry and specialised devices.
